Using structural and evolutionary information to detect and correct pyrosequencing errors in non-coding RNAs

### 2013-05-30 JCB/main_RNAPyro_JCB.tex
Finished outside
Typos
added graphs results
art description
Made the paper 'Arxiv-friendly'

\documentclass{llncs}
\usepackage[top=1.5in, bottom=1.5in,right=1.5in,left=1.5in]{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
%\usepackage{jcompbio}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage{amsthm} %pour les newtheorem
\usepackage{epstopdf}
\usepackage{xspace}
\usepackage{relsize}
\usepackage[numbers]{natbib}
\usepackage[colorinlistoftodos,textsize=small]{todonotes}

@@

\usepackage{tikz}
\usepackage{amsmath}
\usepackage{ifthen}
\usepackage{relsize}
\usetikzlibrary{positioning}
\usetikzlibrary{matrix}
\usetikzlibrary{calc}
\usetikzlibrary{shapes}
\usetikzlibrary{arrows}
\usetikzlibrary{fit}
\usetikzlibrary{decorations}
\usetikzlibrary{snakes}
\usetikzlibrary{shadows}
\pgfdeclarelayer{background}
\pgfdeclarelayer{backbackground}
\pgfdeclarelayer{foreground}
\pgfsetlayers{backbackground,background,main,foreground}

@@

%\title{An inside-outside algorithms for mutant RNAs with applications to error detections in structured RNAs}
\title{Using structural knowledge to correct RNA pyrosequencing errors in non-coding RNAs}
\author{Vladimir Reinharz\inst{1}, Yann Ponty\inst{2}$^{*}$ \and J\'er\^{o}me Waldisp\"{u}hl\inst{1}$^*$}
\date{}
\institute{School of Computer Science, McGill University, Montreal, Canada.
	\and  Laboratoire d'informatique, \'Ecole Polytechnique, Palaiseau, France.
	 \\\email{jeromew@cs.mcgill.ca}, \email{yann.ponty@lix.polytechnique.fr}}

@@

%  \usepackage{hyperref}
%  \hypersetup{colorlinks}
%              citecolor=black,
%              filecolor=black%
%              linkcolor=black%
%              urlcolor=black%
%              pdftex}

@@

\ShowTODO{\setcounter{tocdepth}{1}
\listoftodos} 
\maketitle
%\section{}
%\subsection{}
\begin{abstract}
Analysis of the sequence-structure relationship in RNA molecules are essential to evolutionary studies but also to 
concrete applications such as error-correction methodologies in sequencing technologies. The prohibitive sizes of the
mutational and conformational landscapes combined with the volume of data to proceed require efficient algorithms 
to compute sequence-structure properties. More specifically, here we aim to calculate which mutations increase the most the 
likelihood of a sequence to a given structure and RNA family.\\
In this paper, we introduce \RNApyro, an efficient linear-time and space inside-outside algorithm that computes exact mutational
probabilities under secondary structure and evolutionary constraints given as a multiple sequence alignment with a consensus structure.
We develop a scoring scheme combining classical stacking base pair energies to novel isostericity scales, and apply our techniques
to correct point-wise errors in 5s rRNA sequences. Our results suggest that \RNApyro is a promising algorithm to complement existing
tools in the NGS error-correction pipeline.

>>>>

\documentclass{llncs}
\usepackage[top=1.5in, bottom=1.5in,right=1.5in,left=1.5in]{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
%\usepackage{jcompbio}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage{amsthm} %pour les newtheorem
\usepackage{epstopdf}
\usepackage{xspace}
\usepackage{relsize}
%\usepackage{bbm}
\usepackage{bbold}
\usepackage[numbers]{natbib}
\usepackage[colorinlistoftodos,textsize=small]{todonotes}

\usepackage{caption}
%\usepackage{subcaption}

@@

@@

%\title{An inside-outside algorithms for mutant RNAs with applications to error detections in structured RNAs}
\title{Using structural and evolutionary information to detect and correct pyrosequencing errors in non-coding RNAs}
\author{Vladimir Reinharz\inst{1}, Yann Ponty\inst{2}$^{*}$ \and J\'er\^{o}me Waldisp\"{u}hl\inst{1}$^*$}
\date{}
\institute{School of Computer Science, McGill University, Montreal, Canada.
	\and  Laboratoire d'informatique, \'Ecole Polytechnique, Palaiseau, France.
	 \\\email{jeromew@cs.mcgill.ca}, \email{yann.ponty@lix.polytechnique.fr}}

@@

%  \usepackage{hyperref}
%  \hypersetup{colorlinks}
%              citecolor=black,
%              filecolor=black%
%              linkcolor=black%
%              urlcolor=black%
%              pdftex}
\usepackage{subcaption}
\captionsetup{compatibility=false}

\newcommand{\ART}{\texttt{ART}\xspace}

@@

\ShowTODO{\setcounter{tocdepth}{1}
\listoftodos} 
\maketitle
%\section{}
%\subsection{}
\begin{abstract}
Analysis of the sequence-structure relationship in RNA molecules are essential to evolutionary studies but also to 
concrete applications such as error-correction methodologies in sequencing technologies. The prohibitive sizes of the
mutational and conformational landscapes combined with the volume of data to proceed require efficient algorithms 
to compute sequence-structure properties. More specifically, here we aim to calculate which mutations increase the most the 
likelihood of a sequence to a given structure and RNA family.\\
In this paper, we introduce \RNApyro, an efficient linear-time and space inside-outside algorithm that computes exact mutational
probabilities under secondary structure and evolutionary constraints given as a multiple sequence alignment with a consensus structure.
We develop a scoring scheme combining classical stacking base pair energies to novel isostericity scales, and apply our techniques
to correct point-wise errors in 5s and 16s rRNA sequences. Our results suggest that \RNApyro is a promising algorithm to complement existing
tools in the NGS error-correction pipeline.
